Numerical modelling of the Cordilleran ice sheet

### 2014-08-10 kappa.tex
Move one figure up.
Fix one sentence in the abstract.

However, this maximum stage appears short-lived and out of balance with
contemporaneous climate. During most of the simulated last glacial cycle, the
North American Cordillera is characterized by an intermediate state of
glaciation including isolated glaciers and ice caps covering major mountain
ranges, the largest of which is located over the Skeena Mountains. The numerically modelled Cordilleran ice sheet appears in constant imbalance with evolving climate conditions, while the nature of this transient response transcends the complexity of two-dimensional, conceptual models of ice sheet growth and decay.

>>>>

However, this maximum stage appears short-lived and out of balance with
contemporaneous climate. During most of the simulated last glacial cycle, the
North American Cordillera is characterized by an intermediate state of
glaciation including isolated glaciers and ice caps covering major mountain
ranges, the largest of which is located over the Skeena Mountains. The
numerically modelled Cordilleran ice sheet appears in constant imbalance with
evolving climate conditions, while the complexity of this transient response
transcends that encapsulated in two-dimensional, conceptual models of ice sheet
growth and decay.
